Single-cell virus sequencing of influenza infections that trigger innate immunity

### 2018-09-26 paper/paper.tex
tiny bit more text in Results validation section

\subsection{The full genotypes of viruses in single IFN+ and IFN- cells}

@@

\subsection{Systematic examination of viral features associated with infection outcome}

@@

\subsection{Validation that multiple types of viral mutations increase IFN induction}

@@

To test if the viral defects identified in single IFN+ cells played a causal role in triggering IFN expression, we used reverse genetics to generate bulk stocks of viruses with some of these mutations.
The greatest enrichment of amino-acid substitutions in IFN+ cells was in the PB1 and NS genes (\FIG{mutations}C), so we...

>>>>

\subsection{Full genotypes of viruses infecting single IFN+ and IFN- cells}

@@

\subsection{Viral features associated with infection outcome in single cells}

@@

\subsection{Defects in viruses infecting single IFN+ cells often increase IFN induction}

@@

To test if the viral defects identified in single IFN+ cells play a causal role in triggering IFN expression, we used reverse genetics to generate bulk stocks of viruses with some of these defects.

The viral feature most strongly associated with IFN induction in single cells was failure to express the NS gene (\FIG{genotypes}, \FIG{mutations}C).
Although it is sometimes possible to use complementing cell lines to generate influenza viruses lacking a specific viral gene~\citep{fujii2003selective,marsh2007specific}, we were unsuccessful in using this approach to generate viruses that lacked NS.
The NS gene encodes two proteins (NS1 and NS2), the first of which is influenza virus's primary innate-immune antagonist~\citep{garcia1998influenza, hale2008multifunctional}.
We therefore mimicked the effect of absence of NS by creating a mutant virus (which we will term \emph{NS1stop}) that had multiple stop codons early in the NS1 coding sequence.

The single-cell data also showed that amino-acid substitutions in the PB1 and NS genes were associated with IFN induction (\FIG{genotypes}, \FIG{mutations}C), so we also created mutant viruses for each amino-acid substitution found in these genes among IFN+ cells that did not also lack the NS gene.
Overall, there were six \jdbcomment{actually, seven with S704P} such point mutant viruses: PB1-D27N, PB1-G206S, PB1-K279R, PB1-T677A, \jdbcomment{what about PB1-S704P?} NS1-A122V, and NS2-E47G (\FIGSUPP[genotypes]{genotypes_by_ifn}).
